Canadian Family...

### 2022-03-19 output/paper3.Rmd
fix

```{r include=FALSE}
# Load GSS family data
gss<- read_csv(here::here("input/gss_family.csv"))
gss<-gss%>%select(age,feelings_life,sex,marital_status, average_hours_worked,income_family,income_respondent) %>%
  filter(marital_status == "Married" | marital_status == "Single, never married")
```

@@

# Create a table
gss_cleaned <- gss %>%
  drop_na() %>%
  slice(1:10) %>%
  kable(
    caption = "Extracting the first ten rows from the cleaned GSS Family survey dataset",
col.names=c("Age", "Feelings about life", "Sex", "Marital status", "Average hours worked", "Family income", "Personal income"),
linesep = "", digits = 1, booktabs=TRUE) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 9)
gss_cleaned
```

>>>>

```{r include=FALSE}
# Load GSS family data
gss<- read_csv(here::here("input/gss_family.csv"))
gss <- gss %>% select(age,feelings_life,sex,marital_status, average_hours_worked,income_family,income_respondent, education) %>%
  filter(marital_status == "Married" | marital_status == "Single, never married")
```

@@

# Create a table
gss_cleaned <- gss %>%
  drop_na() %>%
  slice(1:10) %>%
  kable(
    caption = "Extracting the first ten rows from the cleaned GSS Family survey dataset",
col.names=c("Age", "Feelings about life", "Sex", "Marital status", "Average hours worked", "Family income", "Personal income", "Education"),
linesep = "", digits = 1, booktabs=TRUE) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 9)
gss_cleaned
```
